---
title: "Title"
author: "Tom Palmer"
date: '`r Sys.Date()`'
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    code_download: true
    code_folding: show
  pdf_document: default
---

```{r setup, include=FALSE, warning=FALSE, results=FALSE}
# Knit the doc with this option set to TRUE for answers document
# and to FALSE for the questions document
knitr::opts_chunk$set(include = FALSE) 
def.chunk.hook <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(
  chunk = function(x, options) {
    x <- def.chunk.hook(x, options)
    ifelse(
      options$size != "normalsize",
      paste0("\n \\", options$size, "\n\n", x, "\n\n \\normalsize \n"),
      x
    )
  }
)
library(tidyverse)
```

# Introduction

This example R Markdown document demonstrates how to include questions and answers in the same Rmd document.

# Questions

I have designed the question sheet to be compiled as the `pdf_document` output.

When rendering your question document set `knitr::opts_chunk$set(include = FALSE)` in the setup chunk.

Paragraph text for questions is standard R Markdown, which can include $\LaTeX$ maths and code chunks. 

R code chunks in questions for which you want to see the code or output or both require the chunk option `include=TRUE`, i.e.

````
```{r, include=TRUE}`r ''`
...code...
```
````

# Answers

I prefer to render the answers document as the `html_document` output but any output format could be used. 

When rendering your answers document set `knitr::opts_chunk$set(include = TRUE)` in the setup chunk.

Paragraph text for answers go in `asis` code chunks, i.e.

````
```{asis}`r ''`
...Text explaining the answer ...
```
````

```{asis}
Paragraph text for answers.
```

R code chunks for answers are included as normal, i.e.

````
```{r}`r ''`
...Code for answer...
```
````

You can use your preferred R Markdown syntax for laying out your questions. I often use simple section headers, e.g.
```
# Question 1
```

For numbered sections add the option `number_sections: true` to the output in the YAML header.
