---
title: "Generating questions and solutions documents from the same R Markdown document"
author: "Tom Palmer"
date: '`r Sys.Date()`'
params:
  solutions: TRUE
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    code_download: true
    code_folding: show
  pdf_document: default
---

```{r setup, include=FALSE, warning=FALSE, results=FALSE}
# # When doc knitted to html default is to include chunks
# # don't include when latex output
# if (knitr::is_html_output()) {
#   includechunks <- TRUE
# } else { # could use knitr::is_latex_output() here
#   includechunks <- FALSE
# }
knitr::opts_chunk$set(include = params$solutions)

def.chunk.hook <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(
  chunk = function(x, options) {
    x <- def.chunk.hook(x, options)
    ifelse(
      options$size != "normalsize",
      paste0("\n \\", options$size, "\n\n", x, "\n\n \\normalsize \n"),
      x
    )
  }
)
library(tidyverse)
```

# Introduction

- This example R Markdown document demonstrates how to include questions and answers in the same Rmd document.

- When rendering the questions, in the YAML header set `solutions: FALSE`
- When rendering the solutions, in the YAML header set `solutions: TRUE`

# Questions

- To generate pdf output you need the TinyTeX package installed, `install.packages('tinytex')`.

- Paragraph text for questions is written in standard R Markdown syntax, which can include LaTeX maths and code chunks. 

- In questions, R code chunks for which you want to see the code or output or both require the chunk option `include=TRUE`, i.e.
  ````
  ```{r, include=TRUE}`r ''`
  ...code...
  ```
  ````

# Solutions

- I have chosen to render the solutions as the `html_document` output but any output format could be used.

- Paragraph text for solutions go in `asis` code chunks, i.e.
  ````
  ```{asis}`r ''`
  ...Text explaining the answer ...
  ```
  ````

  ```{asis}
  Paragraph text for answers.
  ```

- R code chunks for solutions are included as normal, i.e.
  ````
  ```{r}`r ''`
  ...Code for answer...
  ```
  ````

- You can use your preferred R Markdown syntax for laying out your questions. I often use simple section headers, e.g.
  ```
  # Question 1
  ```

- For numbered sections add the option `number_sections: true` to the output in the YAML header.
